\textbf{The Structure of Chaos: An Empirical Comparison of Fractal Physiology Complexity Indices using NeuroKit2}

### 2022-07-19 analysis.Rmd
edit title in loadings figure

(p2 | p1 | p3) + patchwork::plot_layout(widths = c(1, 2, 1)) +  patchwork::plot_annotation(title = "Computation Time and Factor Loading", theme = theme(plot.title = element_text(hjust = 0.5, face = "bold")))
```

>>>>

(p2 | p1 | p3) + patchwork::plot_layout(widths = c(1, 2, 1)) +  patchwork::plot_annotation(title = "Complexity Indices Computation Time and Factor Loading Profile", theme = theme(plot.title = element_text(hjust = 0.5, face = "bold")))
```
